maxent model avec xvalidation

### 2019-04-04 src/maxent_avec_xvalidation.Rmd
selected model run

```{r train and test on jan inc AIC for reg val}
modelmonth <- cbind(paste0("jan",unique(janprback$year)))
AIClist <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(AIClist$regularization)

@@

    for (i in 1:nrow(AIClist)){
      if(AIClist$regularization[i] == betamval){
      AIClist$Train.AUC[i] <- trainauc
      AIClist$n[i] <- notrainingpoints
      AIClist$coefficients[i] <- nocoeff
      AIClist$sum.of.logs[i] <- sumsamplepred
      AIClist$Test.AUC[i] <- evauc
      AIClist$evcor[i] <- evcor
      AIClist$evpcor[i] <- evpcor
      AIClist$nopresence[i] <- evnp
      AIClist$nobackground[i] <- evna
      AIClist$maxsumsenspec[i] <- evmaxtprtnr
      AIClist$maxsumsenspec[i] <- evmaxkap
      AIClist$no_omission[i] <- evno_omission
      AIClist$equal_sens_spec[i] <- evequal_sens_spec
      AIClist$bic[i] <- bic #not sure this is correct...
      }
    }
  }

AIClist$AIC <- ((2*AIClist$coefficients)-(2*AIClist$sum.of.logs))
AIClist$AICc <- (-2*(AIClist$sum.of.logs)+((2*AIClist$coefficients)*(AIClist$n/(AIClist$n - AIClist$coefficients-1))))

write.csv(AIClist, paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), row.names = FALSE)

@@

@@

    for (i in 1:nrow(AIClist)){
      if(AIClist$regularization[i] == betamval){
      AIClist$Train.AUC[i] <- trainauc
      AIClist$n[i] <- notrainingpoints
      AIClist$coefficients[i] <- nocoeff
      AIClist$sum.of.logs[i] <- sumsamplepred
      AIClist$Test.AUC[i] <- evauc
      AIClist$evcor[i] <- evcor
      AIClist$evpcor[i] <- evpcor
      AIClist$nopresence[i] <- evnp
      AIClist$nobackground[i] <- evna
      AIClist$maxsumsenspec[i] <- evmaxtprtnr
      AIClist$maxsumsenspec[i] <- evmaxkap
      AIClist$no_omission[i] <- evno_omission
      AIClist$equal_sens_spec[i] <- evequal_sens_spec
      AIClist$bic[i] <- bic #not sure this is correct...
      }
    }
  }

AIClist$AIC <- ((2*AIClist$coefficients)-(2*AIClist$sum.of.logs))
AIClist$AICc <- (-2*(AIClist$sum.of.logs)+((2*AIClist$coefficients)*(AIClist$n/(AIClist$n - AIClist$coefficients-1))))

write.csv(AIClist, paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), row.names = FALSE)

>>>>

```{r train and test on jan inc AIC for reg val}
modelmonth <- cbind(paste0("jan",unique(janprback$year)))
aicetc <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(aicetc$regularization)

@@

    for (i in 1:nrow(aicetc)){
      if(aicetc$regularization[i] == betamval){
      aicetc$Train.AUC[i] <- trainauc
      aicetc$n[i] <- notrainingpoints
      aicetc$coefficients[i] <- nocoeff
      aicetc$sum.of.logs[i] <- sumsamplepred
      aicetc$Test.AUC[i] <- evauc
      aicetc$evcor[i] <- evcor
      aicetc$evpcor[i] <- evpcor
      aicetc$nopresence[i] <- evnp
      aicetc$nobackground[i] <- evna
      aicetc$maxsumsenspec[i] <- evmaxtprtnr
      aicetc$maxsumsenspec[i] <- evmaxkap
      aicetc$no_omission[i] <- evno_omission
      aicetc$equal_sens_spec[i] <- evequal_sens_spec
      aicetc$bic[i] <- bic #not sure this is correct...
      }
    }
  }

aicetc$AIC <- ((2*aicetc$coefficients)-(2*aicetc$sum.of.logs))
aicetc$AICc <- (-2*(aicetc$sum.of.logs)+((2*aicetc$coefficients)*(aicetc$n/(aicetc$n - aicetc$coefficients-1))))

write.csv(aicetc, paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), row.names = FALSE)

@@

```{r}
modelmonth <- cbind(paste0("jan",unique(janprback$year)))
aicetc <- read.csv("../data/env/AICcFinalmod.csv", header = TRUE) #pre-created csv file
for (year in 1:nrow(modelmonth)){
  timeslice <- modelmonth[year] #testing timeslice
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(janprback, year != yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  test <-  subset(janprback, year == yr) #creates the testing dataset
  testp <- subset(test, occurrence == "1") #splits the testing dataset into presences
  testp <- subset(testp, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  testb <- subset(test, occurrence == "0") #splits the testing dataset into background
  testb <- subset(testb, select = -c(year, occurrence)) #don't need year and occurrence for modelling
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

  if (timeslice == "jan2003"){
    betaval <- 1
  } else if (timeslice == "jan2004"){
    betaval <- 1
  } else if (timeslice == "jan2005"){
    betaval <- 1.5
  } else if (timeslice == "jan2006"){
    betaval <- 2.25
  }

    mod <- maxent(x = train, p = trainpa, path = paste0("../output/maxent/models/", timeslice), args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", paste0("betamultiplier=", betaval)))

@@

      aicetc$Train.AUC <- trainauc
      aicetc$n[i] <- notrainingpoints
      aicetc$coefficients <- nocoeff
      aicetc$sum.of.logs <- sumsamplepred
      aicetc$Test.AUC <- evauc
      aicetc$evcor <- evcor
      aicetc$evpcor <- evpcor
      aicetc$nopresence <- evnp
      aicetc$nobackground <- evna
      aicetc$maxsumsenspec <- evmaxtprtnr
      aicetc$maxsumsenspec <- evmaxkap
      aicetc$no_omission <- evno_omission
      aicetc$equal_sens_spec <- evequal_sens_spec
      aicetc$bic <- bic #not sure this is correct...
      aicetc$beta <- betaval

aicetc$AIC <- ((2*aicetc$coefficients)-(2*aicetc$sum.of.logs))
aicetc$AICc <- (-2*(aicetc$sum.of.logs)+((2*aicetc$coefficients)*(aicetc$n/(aicetc$n - aicetc$coefficients-1))))

write.csv(aicetc, paste0("../output/maxent/models/", timeslice, "/AICforMaxentReg.csv"), row.names = FALSE)
